### 2018-03-07 Paper/jaccardbaetica.tex
update results' git status

The analysis shows that amphoric stamps are not correlated with spatial distance.

A matrix distance of similarity between workshops can be seen in Fig.1. The matrix displays

Morisita-Horn dissimilarities

A dendrogram was generated

Some closest workshops show a similarity on the stamps such as BLA BLA BLA . This could be due to several reasons.

doesn't support

As summary, these results

@@

No strong similarity between stamps and amphora workshops were found.

There is not connection between stamps and amphora workshops

There is not similar stamps in closest workshop

Similar stamps were not found in closest amphorae workshops so it could be interpreted as no direct connection between stamps and the location of amphora workshops were found.

It could be due to several reason. On the one hand, the use of this amphoric stamps were exclusively running by the owner or family to distinguish the amphora workshop (CITAR). On the other, it could be somehow a batch systematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases.

just 30-40 \% of amphora Dressel 20 was marked 
An any case, 
Considering,

>>>>

The analysis shows that amphoric stamps could not be correlated with spatial distance.

The correlation coefficients range from a minimum to a maximum. The dendrogram shown in Fig. 2 was obtained with Morisita-Horn index. This dendrogram suggests that amphora workshops used different stamps for their prodution system. Accordingly only few closer workshops show a similarity on the stamps while most of them seem to display different stamps roles.

@@

No strong relation between stamps and spatial distance have been detected in amphora workshops.  
The analysis suggests that there is not connection between stamps and the same amphora workshops so similar stamps between closer amphora workshops were not found, excluding certain exception. Consequently the majority of stamps are located in different amphora workshops.

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis. Rather it could be interpreted due to several reason. On the one hand, the use of this amphoric stamps were exclusively running by the owner or family to distinguish the amphora workshop (CITAR). (EXPLICAR)

On the other, it could be somehow a batch systematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases (CITAR).
(EXPLICAR)

%Neither it seems a group of amphora workshops sharing the same stamps.

An any case,

As summary, this method presented here highlights

%Dressel 20 marked in the 30-40\%
